%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemMine}[0]{
  \item{
    
  }
  \vspace{-2pt}
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r} 
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingMine}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.0\textwidth}{l@{\extracolsep{\fill}}l}
      \textbf{#1} \\
      \textit{#2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Raghuvar Arora}} \\
  \href{https://www.linkedin.com/in/raghuvar-arora/}{Linkedin: linkedin.com/in/raghuvar-arora/} & Email: \href{mailto:}{raghuvararora@gmail.com} \\
  \href{https://github.com/raghuvar-arora-au2}{Github: ~~github.com/raghuvar-arora-au2} & Mobile:~~~+91-750-8895-238 \\
\end{tabular*}




\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Security Analyst\textbf{/}IAM developer}{Remote}
    {Ernst \& Young ( EY )}{Oct 2020 - Apr 2022}
    \resumeItemListStart
        \resumeItemMine
           Primarily involved in designing and \textbf{implementing} IAM solutions (Sailpoint IIQ) using Java/Beanshell.
          \resumeItemMine
          Responsible for developing workﬂows for the automation of Lifecycle Events.
          \resumeItemMine 
          Wrote a \textbf{universal framework} for streamlining integration of JDBC based applications to the IIQ.
          \resumeItemMine 
          Involved in the direct integration of target applications including Active Directory, JDBC, Web service apps , etc.
          \resumeItemMine 
          Contributed to the preparation of the detailed design documents to depict the IAM design that has to be implemented for the customer.
          \resumeItemMine 
          Involved in POC projects to implement Data privacy systems, and numerous \textbf{complex use cases}.
          \resumeItemMine 
          \textbf{Tech Stack}: Java, Apache Tomcat, Azure suite, SailPoint IIQ, MS-SQL, Jersey.
      \resumeItemListEnd
\vspace{0pt}
    \resumeSubheading
		{Full-stack Developer}{Remote}
		{ Toy Ventures inc. }{Jul 2020 -  Oct 2020}
		\resumeItemListStart
            \resumeItemMine
           Worked on the hybrid app ACNH exchange (defunct now) that has more than \textbf{1,000,000 downloads} on Android and Apple store, combined.
        \resumeItemMine
           \textbf{Reduced} the average queue turnaround time \textbf{by   $\sim$ 30\%} by leveraging FireBase Cloud Messaging
        \resumeItemMine
           Added support for localization and numerous UX/UI improvements. Also worked on \textbf{enabling moderation}.
           \resumeItemMine
           \textbf{Tech stack}: Python, React, Ionic, Flask, PostgreSQL, Redis, EC2
		\resumeItemListEnd
\vspace{0pt}
    \resumeSubheading
		{Student Researcher}{}
		{ Guru Nanak Dev University }{Jun 2019 - Apr 2020}
		\resumeItemListStart
            \resumeItemMine
           Assisted Dr Munish Saini at the department of Computer Eng. and Technology
        \resumeItemMine
           Worked on projects related to NLP, speciﬁcally sementic analysis, and Software engineering metrics.
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------

\vspace{-5pt}
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheadingMine{MarkIT-up }
    {JQuery, NodeJS, MongoDB, Heroku, JavaScript ES6, Github Actions }
    \resumeItemListStart
        \resumeItemMine\href{https://github.com/raghuvar-arora-au2/markit_personal-diary}{github}
           Journaling app with \textbf{markdown} support, and provides the ability to \textbf{create directories}.
          \resumeItemMine
          Renders (Github Flavoured)HTML/formated text from plain text or markdown in real-time
          \resumeItemMine 
          Leverages \textbf{Facebook OAuth2.0 SDK} for authentication, Github Action for CI/CD, and deployed on Heroku

      \resumeItemListEnd
\vspace{0pt}
    \resumeSubheadingMine
		{Audacity.ai }
		{Python, Flask, Wit.ai, Chatteron}
		\resumeItemListStart
            \resumeItemMine
          A chatbot with numerous features like \textbf{location sharing}, and fetching nearby places of relevance.
        \resumeItemMine
           Uses Chatteron framework which supports NLP and allows easy deployment across multiple social media platforms.
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\begin{Education}
\section{Education}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Nanak Dev University}{Amritsar, Punjab}
      {Bachelor of Technology - Computer Science and Engineering ;  GPA: 7.81}{August 2016 - June 2020}
    \resumeSubHeadingListEnd
\end{Education}   
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Python, JavaScript, SQL, Bash, Java, Beanshell}
	\resumeSubItem{Tools/Frameworks}{Git, Selenium, AWS S3, EC2, Redis, Tableau, FCM, Django, React, Spring, Kafka}
	\resumeSubItem{DBMS}{MongoDB, MySQL, PostgreSQL, SQL, NoSQL}
\resumeSubHeadingListEnd

\vspace{-5pt}
%-----------Awards-----------------
\section{Research \& Publications}
\begin{description}[font=$\bullet$, leftmargin=10pt]
\item {(Journal) M. Saini, \textbf{R. Arora}, A. Oyeniyi, "In-depth Analysis and Prediction of Coupling Metrics of Open Source
Software Projects", Journal of Information Technology Research, Vol 15, issue 4.}
\vspace{-5pt}
\item {(Conference) D. Gargi and \textbf{R. Arora}, "SeqGAN-APG: Sequential Generative Adversarial Networks for Automatic
Patch Generation," \textbf{(IEEE)} Smart Technologies, Communication and Robotics, 2021, pp. 1-7 }

\end{description}

\vspace{-7pt}
\section{Volunteer Experience}
 \begin{description}[font=$\bullet$, leftmargin=10pt, ]
\item {Active participant on online coding platforms(Hackerrank, leetcode)}
\vspace{-5pt}
\item {\textbf{Mentored} over 20 younger students in several web development technologies.}
\vspace{-5pt}
\item{
Worked as a Subject Expert on Chegg.com with over 300 solved queries related to computer science subjects.}
\end{description}

\end{document}